%-------------------------
% Resume in Latex
% Author : Richard So
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% nth
\usepackage[super]{nth}

% sane underline
\usepackage{contour}
\usepackage[normalem]{ulem}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
  \item\small{
      {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  {\Huge \scshape \href{https://sorichard.com}{Richard So}} \\ \vspace{4pt}
  \small \faPhone\ (347) 281-3815 ~
  \href{mailto:richardso2021@gmail.com}{\faEnvelope\ \myuline{richardso2021@gmail.com}} ~
  \href{https://linkedin.com/in/richardso21/}{\faLinkedin\ \myuline{in/richardso21}}  ~
  \href{https://github.com/richardso21}{\faGithub\ \myuline{@richardso21}}  ~
  \href{https://sorichard.com}{\faGlobeAmericas\ \myuline{sorichard.com}}
  \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Georgia Institute of Technology}{August 2021 -- May 2024}
{College of Computing | B.S. in Computer Science}{Atlanta, GA}
\resumeItemListStart
\resumeItem{Threads: Intelligence \& People; GPA: 4.0}
\resumeItemListEnd
% \resumeSubheading
% {Staten Island Technical High School}{September 2017 -- June 2021}
% {Thomas P. DiNapoli New York State Comptroller Achievement Award}{Staten Island, NY}
\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
                \textbf{Programming Languages} $|$ {Java, Python, JavaScript, TypeScript, MATLAB, SQL, C/C++} \\
                \textbf{Frameworks \& Libraries} $|$ {Vue, Nuxt, Angular, Flask, Electron, NumPy, Pandas, Matplotlib, PyTorch, XGBoost} \\
                \textbf{Technologies} $|$ {Git, Vim, REST, Firebase, PostgreSQL, SQLite, Teradata, Salesforce, CRM Analytics} \\
                % \textbf{Web Development} $|$ {Git/Github, Vue, React, Flask, REST, Firebase} \\
                % \textbf{Machine Learning} $|$ {NumPy, Pandas, Matplotlib, PyTorch, TensorFlow/Keras} \\
                % \textbf{Data Handling/Analysis} $|$ {PostgreSQL, Microsoft Access, Salesforce, Tableau CRM} \\
                \textbf{Relevant Coursework} $|$ {Java OOP, Data Structures \& Algorithms, Computer Organization, Objects \& Design} \\
          }}
\end{itemize}
\vspace{-16pt}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Union Pacific Railroad}{May 2022 - August 2022}
{Software Development Intern}{Omaha, NE}
\resumeItemListStart
\resumeItem{Leveraged Salesforce CRM Analytics \& XGBoost to generate rail shipment pricing models with up to 99\% accuracy.}
\resumeItem{Decreased the error margin of price estimations by 31\% versus an existing \nth{3} party pricing analytics solution.}
\resumeItem{Created an Angular web application to query/fetch price predictions from the Einstein Prediction Service API.}
\resumeItem{Strengthened team collaboration and effective demonstration abilities under an Agile workflow environment.}
\resumeItemListEnd
\resumeSubheading
{EPIC Lab - Georgia Institute of Technology}{January 2022 - Present}
{Undergraduate Research Assistant}{Atlanta, GA}
\resumeItemListStart
\resumeItem{Analyzed experimental data using Matlab in a project to optimize hip exoskeleton controls for human movement.}
\resumeItem{Programmed a pipeline for multi-dimensional data collected from EMG and metabolics measurement sensors.}
\resumeItem{Maintained a codebase to visualize muscle activity and metabolic cost differences between trial conditions.}
\resumeItemListEnd
\resumeSubheading
{Brooklyn College CUNY}{July 2019 - September 2021}
{Researcher}{Brooklyn, NY}
\resumeItemListStart
\resumeItem{Performed research on machine learning applications under Dr. Michael I Mandel at Brooklyn College CUNY.}
\resumeItem{Optimized an existing bird audio detection model to be over 90\% accurate using the PCEN audio preprocessor.}
\resumeItem{Utilized foreground segmentation techniques to automatically predict the presence of animals in image data.}
\resumeItem{Familiarized with data wrangling and visualization approaches using the Pandas and Matplotlib Python libraries.}
\resumeItemListEnd
\resumeSubheading
{Staten Island Technical High School}{June 2021 - August 2021}
{Computer Science Curriculum Designer}{Staten Island, NY}
\resumeItemListStart
% \resumeItem{Curated a collection of course materials (lessons \& exercises) for the school's Computer Science courses.}
\resumeItem{Curated multiple project tracks to solidify industry-standard HTML, CSS, and JavaScript skills for students.}
\resumeItem{Expanded the existing curriculum to include the MEVN (MongoDB, Express, Vue, NodeJS) technology stack.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt} \resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{eyePause Desktop Application Utility} $|$ \textit{TypeScript, Electron} \ \href{https://www.github.com/richardso21/eyePause-2}{\faGithub}}{July 2022}
\resumeItemListStart
\resumeItem{Engineered a desktop application to track screen-on time and assist users in taking regular breaks from the device.}
\resumeItem{Developed using the Electron framework and TypeScript language under the hood.}
\resumeItemListEnd
\vspace{-13pt}
\resumeProjectHeading
{\textbf{Staten Island Solar Car Telemetry System} $|$ \textit{C++, PlatformIO, SQLite} \ \href{https://www.github.com/richardso21/SITHS-SolarCar}{\faGithub}}{June 2021}
\resumeItemListStart
\resumeItem{Implemented a real-time solution to track and transmit solar car vital data to a local database.}
\resumeItem{Programmed Arduino microcontrollers to manage multiple hardware modules (GPS, LoRa Radio, LCD, \& ADC).}
\resumeItemListEnd
\vspace{-13pt}
\resumeProjectHeading
{\textbf{Full-Stack Recipe Sharing Application} $|$ \textit{JavaScript, Nuxt, Firebase} \ \href{https://www.github.com/richardso21/bone-apple-teeth}{\faGithub}}{May 2021}
\resumeItemListStart
\resumeItem{Constructed a server-side rendered application for users to post and view food recipes using Nuxt.js.}
\resumeItem{Binded Firebase Authorization, Cloud Firestore, and Storage services to a responsive frontend interface.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}


%-----------AWARDS/ACHIEVEMENTS---------------
\section{Awards \& Achievements}
\resumeSubHeadingListStart
\resumeSubSubheading{}{}
\vspace{-15pt}
\resumeItemListStart
\resumeItem{Co-Author of a \href{https://ieeexplore.ieee.org/document/9053338}{\myuline{2020 IEEE ICASSP conference paper}} featuring my research on ML for bird audio detection.}
\resumeItem{Cultivated over 500,000 viewers of my technology/programming blog on \href{https://richardso21.medium.com/}{\myuline{Medium}}.}
\resumeItem{Winner of the \href{https://youtu.be/BKwb6yks85o}{\myuline{Milton Fisher Scholarship for Innovation and Creativity.}}}
\resumeItem{\nth{1} Award Winner of the 2020 TNYC STEM Fair.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\end{document}
